A Comparison of Regression models for Cylindrical data in Psychology.

### 2018-09-24 Manuscript/Plots/dataplot.tex
Plots update

% Created by tikzDevice version 0.11 on 2018-07-02 13:49:21
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

>>>>

% Created by tikzDevice version 0.11 on 2018-09-21 15:13:32
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.24,162.19) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.15,153.45) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (131.49,124.69) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.79,142.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (107.31,176.35) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (296.78,196.40) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (321.82,144.06) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.05,133.33) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.37,133.13) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (274.47,146.33) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (258.79,150.22) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.75,146.76) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (291.49,140.22) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (313.42,144.38) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.70,144.86) circle (  2.25);

### 2018-09-24 Manuscript/Plots/reglinediffSE.tex
Plots update

% Created by tikzDevice version 0.11 on 2018-07-02 13:49:26
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (345.67,137.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.00,198.47) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (274.40,142.46) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (369.43,141.10) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (310.04,138.00) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (369.43,141.81) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (321.92,154.36) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (369.43,141.28) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.16,137.58) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (310.04,164.72) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (357.55,147.90) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.16,136.34) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (286.28,157.43) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (286.28,147.59) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (310.04,140.02) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (357.55,154.03) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.00,136.81) circle (  2.25);

@@

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 10.80,132.47) {$\theta_{test}$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,252.94);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20, 72.87) -- ( 49.20,193.08);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20,193.08) -- ( 43.20,193.08);

@@

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 34.80,193.08) {160};
\end{scope}
\begin{scope}
\path[clip] ( 49.20, 61.20) rectangle (408.42,203.75);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 62.50,143.08) --
	( 67.26,143.04) --
	( 72.01,143.00) --
	( 76.76,142.96) --
	( 81.51,142.91) --
	( 86.26,142.87) --
	( 91.01,142.83) --
	( 95.77,142.78) --
	(100.52,142.74) --
	(105.27,142.70) --
	(110.02,142.66) --
	(114.77,142.61) --
	(119.52,142.57) --
	(124.28,142.53) --
	(129.03,142.48) --
	(133.78,142.44) --
	(138.53,142.40) --
	(143.28,142.35) --
	(148.03,142.31) --
	(152.78,142.27) --
	(157.54,142.23) --
	(162.29,142.18) --
	(167.04,142.14) --
	(171.79,142.10) --
	(176.54,142.05) --
	(181.29,142.01) --
	(186.05,141.97) --
	(190.80,141.92) --
	(195.55,141.88) --
	(200.30,141.84) --
	(205.05,141.80) --
	(209.80,141.75) --
	(214.56,141.71) --
	(219.31,141.67) --
	(224.06,141.62) --
	(228.81,141.58) --
	(233.56,141.54) --
	(238.31,141.49) --
	(243.06,141.45) --
	(247.82,141.41) --
	(252.57,141.36) --
	(257.32,141.32) --
	(262.07,141.28) --
	(266.82,141.24) --
	(271.57,141.19) --
	(276.33,141.15) --
	(281.08,141.11) --
	(285.83,141.06) --
	(290.58,141.02) --
	(295.33,140.98) --
	(300.08,140.93) --
	(304.84,140.89) --
	(309.59,140.85) --
	(314.34,140.81) --
	(319.09,140.76) --
	(323.84,140.72) --
	(328.59,140.68) --
	(333.34,140.63) --
	(338.10,140.59) --
	(342.85,140.55) --
	(347.60,140.50) --
	(352.35,140.46) --
	(357.10,140.42) --
	(361.85,140.37) --
	(366.61,140.33) --
	(371.36,140.29) --
	(376.11,140.25) --
	(380.86,140.20) --
	(385.61,140.16) --
	(390.36,140.12) --
	(395.12,140.07) --
	(399.87,140.03) --
	(404.62,139.99) --
	(409.37,139.94) --
	(414.12,139.90) --
	(418.87,139.86) --
	(423.63,139.82) --
	(428.38,139.77) --
	(433.13,139.73) --
	(433.62,139.72);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 62.50, 83.63) --
	( 67.26, 83.75) --
	( 72.01, 83.88) --
	( 76.76, 84.03) --
	( 81.51, 84.19) --
	( 86.26, 84.36) --
	( 91.01, 84.55) --
	( 95.77, 84.76) --
	(100.52, 85.00) --
	(105.27, 85.26) --
	(110.02, 85.56) --
	(114.77, 85.89) --
	(119.52, 86.28) --
	(124.28, 86.72) --
	(129.03, 87.24) --
	(133.78, 87.85) --
	(138.53, 88.58) --
	(143.28, 89.47) --
	(148.03, 90.56) --
	(152.78, 91.93) --
	(157.54, 93.68) --
	(162.29, 95.97) --
	(167.04, 99.01) --
	(171.79,103.02) --
	(176.54,108.14) --
	(181.29,114.10) --
	(186.05,120.11) --
	(190.80,125.34) --
	(195.55,129.48) --
	(200.30,132.62) --
	(205.05,134.98) --
	(209.80,136.79) --
	(214.56,138.19) --
	(219.31,139.31) --
	(224.06,140.22) --
	(228.81,140.96) --
	(233.56,141.58) --
	(238.31,142.11) --
	(243.06,142.56) --
	(247.82,142.95) --
	(252.57,143.30) --
	(257.32,143.60) --
	(262.07,143.86) --
	(266.82,144.10) --
	(271.57,144.32) --
	(276.33,144.51) --
	(281.08,144.69) --
	(285.83,144.85) --
	(290.58,144.99) --
	(295.33,145.13) --
	(300.08,145.25) --
	(304.84,145.36) --
	(309.59,145.47) --
	(314.34,145.57) --
	(319.09,145.66) --
	(323.84,145.75) --
	(328.59,145.83) --
	(333.34,145.90) --
	(338.10,145.97) --
	(342.85,146.04) --
	(347.60,146.10) --
	(352.35,146.16) --
	(357.10,146.22) --
	(361.85,146.27) --
	(366.61,146.32) --
	(371.36,146.37) --
	(376.11,146.42) --
	(380.86,146.46) --
	(385.61,146.50) --
	(390.36,146.54) --
	(395.12,146.58) --
	(399.87,146.62) --
	(404.62,146.65) --
	(409.37,146.68) --
	(414.12,146.72) --
	(418.87,146.75) --
	(423.63,146.78) --
	(428.38,146.80) --
	(433.13,146.83) --
	(433.62,146.83);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] (179.31,112.20) --
	(183.81,112.20) --
	(183.81,116.70) --
	(179.31,116.70) --
	cycle;
\end{scope}
\end{tikzpicture}

>>>>

% Created by tikzDevice version 0.11 on 2018-08-10 10:45:22
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (274.40,163.42) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (321.92,154.46) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.13,124.99) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (286.28,143.66) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.88,177.93) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (238.76,198.47) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (310.04,144.84) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.16,133.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (262.52,133.65) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (321.92,147.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (274.40,151.15) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (321.92,147.61) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (274.40,140.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (345.67,145.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.79,145.66) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (345.67,137.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.00,198.46) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (274.40,142.45) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (369.43,141.09) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (310.04,137.99) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (369.43,141.80) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (321.92,154.35) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (369.43,141.27) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.16,137.57) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (310.04,164.71) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (357.55,147.89) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.16,136.33) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (286.28,157.42) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (286.28,147.58) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (310.04,140.01) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (357.55,154.02) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.00,136.80) circle (  2.25);

@@

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 10.80,132.47) {$\theta$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,252.94);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20, 72.87) -- ( 49.20,193.07);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20,193.07) -- ( 43.20,193.07);

@@

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 34.80,193.07) {160};
\end{scope}
\begin{scope}
\path[clip] ( 49.20, 61.20) rectangle (408.42,203.75);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 62.50,143.08) --
	( 67.26,143.04) --
	( 72.01,143.00) --
	( 76.76,142.96) --
	( 81.51,142.91) --
	( 86.26,142.87) --
	( 91.01,142.83) --
	( 95.77,142.78) --
	(100.52,142.74) --
	(105.27,142.70) --
	(110.02,142.65) --
	(114.77,142.61) --
	(119.52,142.57) --
	(124.28,142.53) --
	(129.03,142.48) --
	(133.78,142.44) --
	(138.53,142.40) --
	(143.28,142.35) --
	(148.03,142.31) --
	(152.78,142.27) --
	(157.54,142.22) --
	(162.29,142.18) --
	(167.04,142.14) --
	(171.79,142.10) --
	(176.54,142.05) --
	(181.29,142.01) --
	(186.05,141.97) --
	(190.80,141.92) --
	(195.55,141.88) --
	(200.30,141.84) --
	(205.05,141.79) --
	(209.80,141.75) --
	(214.56,141.71) --
	(219.31,141.67) --
	(224.06,141.62) --
	(228.81,141.58) --
	(233.56,141.54) --
	(238.31,141.49) --
	(243.06,141.45) --
	(247.82,141.41) --
	(252.57,141.36) --
	(257.32,141.32) --
	(262.07,141.28) --
	(266.82,141.23) --
	(271.57,141.19) --
	(276.33,141.15) --
	(281.08,141.11) --
	(285.83,141.06) --
	(290.58,141.02) --
	(295.33,140.98) --
	(300.08,140.93) --
	(304.84,140.89) --
	(309.59,140.85) --
	(314.34,140.80) --
	(319.09,140.76) --
	(323.84,140.72) --
	(328.59,140.68) --
	(333.34,140.63) --
	(338.10,140.59) --
	(342.85,140.55) --
	(347.60,140.50) --
	(352.35,140.46) --
	(357.10,140.42) --
	(361.85,140.37) --
	(366.61,140.33) --
	(371.36,140.29) --
	(376.11,140.24) --
	(380.86,140.20) --
	(385.61,140.16) --
	(390.36,140.12) --
	(395.12,140.07) --
	(399.87,140.03) --
	(404.62,139.99) --
	(409.37,139.94) --
	(414.12,139.90) --
	(418.87,139.86) --
	(423.63,139.81) --
	(428.38,139.77) --
	(433.13,139.73) --
	(433.62,139.72);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 62.50, 84.15) --
	( 67.26, 84.27) --
	( 72.01, 84.40) --
	( 76.76, 84.54) --
	( 81.51, 84.69) --
	( 86.26, 84.85) --
	( 91.01, 85.03) --
	( 95.77, 85.23) --
	(100.52, 85.45) --
	(105.27, 85.69) --
	(110.02, 85.96) --
	(114.77, 86.27) --
	(119.52, 86.62) --
	(124.28, 87.01) --
	(129.03, 87.47) --
	(133.78, 87.99) --
	(138.53, 88.61) --
	(143.28, 89.35) --
	(148.03, 90.24) --
	(152.78, 91.33) --
	(157.54, 92.68) --
	(162.29, 94.40) --
	(167.04, 96.61) --
	(171.79, 99.50) --
	(176.54,103.26) --
	(181.29,108.01) --
	(186.05,113.56) --
	(190.80,119.29) --
	(195.55,124.47) --
	(200.30,128.70) --
	(205.05,131.98) --
	(209.80,134.49) --
	(214.56,136.43) --
	(219.31,137.94) --
	(224.06,139.14) --
	(228.81,140.12) --
	(233.56,140.92) --
	(238.31,141.59) --
	(243.06,142.16) --
	(247.82,142.65) --
	(252.57,143.07) --
	(257.32,143.44) --
	(262.07,143.77) --
	(266.82,144.05) --
	(271.57,144.31) --
	(276.33,144.54) --
	(281.08,144.75) --
	(285.83,144.94) --
	(290.58,145.11) --
	(295.33,145.26) --
	(300.08,145.41) --
	(304.84,145.54) --
	(309.59,145.66) --
	(314.34,145.78) --
	(319.09,145.88) --
	(323.84,145.98) --
	(328.59,146.07) --
	(333.34,146.16) --
	(338.10,146.24) --
	(342.85,146.32) --
	(347.60,146.39) --
	(352.35,146.45) --
	(357.10,146.52) --
	(361.85,146.58) --
	(366.61,146.63) --
	(371.36,146.69) --
	(376.11,146.74) --
	(380.86,146.79) --
	(385.61,146.84) --
	(390.36,146.88) --
	(395.12,146.92) --
	(399.87,146.96) --
	(404.62,147.00) --
	(409.37,147.04) --
	(414.12,147.07) --
	(418.87,147.11) --
	(423.63,147.14) --
	(428.38,147.17) --
	(433.13,147.20) --
	(433.62,147.21);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] (184.93,112.69) --
	(189.43,112.69) --
	(189.43,117.19) --
	(184.93,117.19) --
	cycle;
\end{scope}
\end{tikzpicture}

### 2018-09-24 Manuscript/Plots/survivaldiffSE.tex
Plots update

% Created by tikzDevice version 0.11 on 2018-07-02 13:49:30
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 62.50,198.47) --
	( 79.14,198.43) --
	( 95.77,198.15) --
	(112.40,197.32) --
	(129.03,195.59) --
	(145.66,192.64) --
	(162.29,188.17) --
	(178.92,181.98) --
	(195.55,173.98) --
	(212.18,164.25) --
	(228.81,153.04) --
	(245.44,140.78) --
	(262.07,128.04) --
	(278.70,115.47) --
	(295.33,103.70) --
	(311.96, 93.25) --
	(328.59, 84.49) --
	(345.22, 77.56) --
	(361.85, 72.41) --
	(378.49, 68.82) --
	(395.12, 66.48);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,252.94);
\definecolor{drawColor}{RGB}{0,0,0}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20, 63.51) -- ( 49.20,198.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20, 63.51) -- ( 43.20, 63.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20, 90.50) -- ( 43.20, 90.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20,117.49) -- ( 43.20,117.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20,144.48) -- ( 43.20,144.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20,171.47) -- ( 43.20,171.47);

@@

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 34.80, 63.51) {0.0};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 34.80, 90.50) {0.2};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 34.80,117.49) {0.4};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 34.80,144.48) {0.6};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 34.80,171.47) {0.8};

@@

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 62.50,198.47) --
	( 79.14,198.44) --
	( 95.77,198.21) --
	(112.40,197.48) --
	(129.03,195.93) --
	(145.66,193.23) --
	(162.29,189.08) --
	(178.92,183.22) --
	(195.55,175.55) --
	(212.18,166.08) --
	(228.81,155.03) --
	(245.44,142.81) --
	(262.07,129.97) --
	(278.70,117.17) --
	(295.33,105.08) --
	(311.96, 94.28) --
	(328.59, 85.19) --
	(345.22, 77.97) --
	(361.85, 72.61) --
	(378.49, 68.89) --
	(395.12, 66.48);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 1pt off 3pt ,line join=round,line cap=round] ( 62.50,198.47) --
	( 79.14,198.44) --
	( 95.77,198.23) --
	(112.40,197.56) --
	(129.03,196.11) --
	(145.66,193.55) --
	(162.29,189.57) --
	(178.92,183.91) --
	(195.55,176.42) --
	(212.18,167.10) --
	(228.81,156.16) --
	(245.44,143.97) --
	(262.07,131.08) --
	(278.70,118.15) --
	(295.33,105.89) --
	(311.96, 94.89) --
	(328.59, 85.60) --
	(345.22, 78.22) --
	(361.85, 72.73) --
	(378.49, 68.93) --
	(395.12, 66.48);

@@

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (331.33,171.02) {mean(SE)};

>>>>

% Created by tikzDevice version 0.11 on 2018-09-18 14:43:22
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 62.50,198.47) --
	( 79.14,198.38) --
	( 95.77,197.84) --
	(112.40,196.49) --
	(129.03,194.01) --
	(145.66,190.14) --
	(162.29,184.70) --
	(178.92,177.62) --
	(195.55,168.93) --
	(212.18,158.83) --
	(228.81,147.63) --
	(245.44,135.76) --
	(262.07,123.72) --
	(278.70,112.05) --
	(295.33,101.23) --
	(311.96, 91.68) --
	(328.59, 83.63) --
	(345.22, 77.20) --
	(361.85, 72.33) --
	(378.49, 68.84) --
	(395.12, 66.48);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,252.94);
\definecolor{drawColor}{RGB}{0,0,0}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20, 62.99) -- ( 49.20,198.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20, 62.99) -- ( 43.20, 62.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20, 90.08) -- ( 43.20, 90.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20,117.18) -- ( 43.20,117.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20,144.27) -- ( 43.20,144.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20,171.37) -- ( 43.20,171.37);

@@

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 34.80, 62.99) {0.0};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 34.80, 90.08) {0.2};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 34.80,117.18) {0.4};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 34.80,144.27) {0.6};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 34.80,171.37) {0.8};

@@

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 62.50,198.47) --
	( 79.14,196.04) --
	( 95.77,190.46) --
	(112.40,182.63) --
	(129.03,173.19) --
	(145.66,162.73) --
	(162.29,151.74) --
	(178.92,140.68) --
	(195.55,129.91) --
	(212.18,119.75) --
	(228.81,110.39) --
	(245.44,101.97) --
	(262.07, 94.57) --
	(278.70, 88.20) --
	(295.33, 82.82) --
	(311.96, 78.36) --
	(328.59, 74.74) --
	(345.22, 71.84) --
	(361.85, 69.57) --
	(378.49, 67.81) --
	(395.12, 66.48);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 1pt off 3pt ,line join=round,line cap=round] ( 62.50,198.47) --
	( 79.14,198.08) --
	( 95.77,196.53) --
	(112.40,193.46) --
	(129.03,188.72) --
	(145.66,182.27) --
	(162.29,174.23) --
	(178.92,164.82) --
	(195.55,154.36) --
	(212.18,143.26) --
	(228.81,131.93) --
	(245.44,120.83) --
	(262.07,110.32) --
	(278.70,100.74) --
	(295.33, 92.29) --
	(311.96, 85.12) --
	(328.59, 79.23) --
	(345.22, 74.56) --
	(361.85, 70.98) --
	(378.49, 68.35) --
	(395.12, 66.47);

@@

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (331.33,171.02) {median(SE)};
